\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-13 manuscript/manuscript.tex
new tables in manuscript

\input{tables/mc_pvals}

@@

The p-values of our test when applied to Microsoft stock return data using
different settings are showcased in Table~\ref{table:microsoft}.
We observe that when the duration of time is large, our method rejects the null
hypothesis unless the degrees of freedom specified is very precise. When
we use 25 years of data, the method
only fails to reject the null hypothesis at $\alpha = .05$ when 
the hypothesized $v = 2.2$, when 
the precision
is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
hundredths place.
When using only 5 years of data, the method reaches a p-value of 
$0.05$ when the hypothesized $v = 2.5$, but the p-value is
lower for $v = 2.2$ and $v = 2.15$.
When we only use 1 year of data, the method fails to reject the null hypothesis
even when the hypothesized distribution family is normal ($v \to \infty$). The
p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
is lower for smaller values of $v$ when using only 1 year of data.

>>>>

\input{tables/mc_pval_1y}

\input{tables/mc_pval_2y}

\input{tables/mc_pval_3y}

\input{tables/mc_pval_4y}

\input{tables/mc_pval_5y}

@@

The p-values of our test when applied to Microsoft stock return data using
different settings are showcased in 
Tables~\ref{table:microsoft1}--\ref{table:microsoft2}.
We observe that when the duration of time is large, our method rejects the null
hypothesis unless the degrees of freedom specified is very precise. When
we use 25 years of data, the method
only fails to reject the null hypothesis at $\alpha = .05$ when 
the hypothesized $v = 2.2$, when 
the precision
is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
hundredths place.
When using only 5 years of data, the method reaches a p-value of 
$0.05$ when the hypothesized $v = 2.5$, but the p-value is
lower for $v = 2.2$ and $v = 2.15$.
When we only use 1 year of data, the method fails to reject the null hypothesis
even when the hypothesized distribution family is normal ($v \to \infty$). The
p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
is lower for smaller values of $v$ when using only 1 year of data.
